---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
```

## 5

```{r}
library(tidyverse)
copier <- read.table('copier.txt', header = TRUE)
head(copier, 5)
```


**(a)** Predictor = Service / Response variable = Minutes 


**(b)** The time spent by the service person seems to be proportional to the time spent by the service person.

```{r}
ggplot(copier, aes(x=Serviced, y=Minutes)) +
  geom_point()
```

**(c)** According to the plot, we can find out that there seems to be a high correlation between two variables.


**(d)** When we take a look at the plot, there seems to be a linear relationship between two variables, and according to corrleation, data, there is 0.978517 correlation between two. Therefore, it is reasonable to judge that they are highly correlated. 

```{r}
cor(copier$Serviced, copier$Minutes)
```

**(e)** $\beta_1 = 15.0352, \beta_0 = -0.5802, R^2 = 0.9575, o^2 = 8.914$

```{r}
copier_result <- lm(Minutes ~ Serviced, data = copier)
summary(copier_result)
```

**(f)**  As $\beta_1 = 15.0352$, every one unit increase of copier machine will lead to an increase of 15.0352 minutes, which is plausible. However, $\beta_0 = -0.5802$ means using 0 copier machine leads to -0.5802 minutes spent, which is impossible in real world settings.


**(g)** $H_0: \beta_1 = 0$, $H_a: \beta_1 \neq 0$

- F-statistic: 968.66

- p-value: 2.2e-16 * 2 = 4.4e-16**

- According to the result, we can conclude that as p-value is less than 0.05, we can reject the null hypothesis that $ \beta_1 = 0$.

```{r}
copier_anova <- anova(copier_result)
copier_anova
```


**(h)** 5 copiers 95% CI: (56.42133, 92.77084)

```{r}
copier_data <- data.frame(Serviced = 5)

predict(copier_result, copier_data, level = 0.95, interval = "prediction")
```



**(i)** Residual, which is equivalent to error between  $y_1, \hat{y}_1$ ** is -9.4902.


```{r}
y_1 <- copier[1,1]
yhat_1 <- 15.0352 * 2 - 0.5802

residual_1 <- y_1 - yhat_1
residual_1
```
