---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
```

## 3

```{r}
library(tidyverse)
covid <- read.csv('UScovid.csv')
```


**(a)** 

```{r}
state.level <- covid %>% filter(date == '2021-06-03') %>% 
  group_by(state) %>% 
  summarize(tot_cases = sum(cases),tot_deaths = sum(deaths))

head(state.level, 6)
```

**(b)** 

```{r}
state.level <- state.level %>%
  mutate(state.rate =   round(100*tot_deaths / tot_cases, 2))
state.level
```

**(c)** A fatality rate of Virginia is 1.66%.
```{r}
state.level %>% filter(state == 'Virginia')
```

**(d)** As we do not have info on total deaths of Puerto Rico, so we also do not know about fatality rate. 

```{r}
state.level %>% filter(state == 'Puerto Rico')
```

**(e)** New Jersey, Massachusetts, New York, Conneticut, DC, Mississippi, Pennsylvania, Louisiana, New Mexico, Maryland

```{r}
head(state.level %>% arrange(desc(state.rate)), 10)
```

**(f)** Alaska, Utah, Virgin Islands, Vermont, Nebraska, Idaho, Northern Marina Islands, Wisconsin, Wyoming, Colorado
```{r}
head(state.level %>% arrange(state.rate), 10)
```

**(g)** 

```{r}
state_pop_election <- read.csv('State_pop_election.csv')
names(state_pop_election)[1] <- "state"

total_df <- full_join(state_pop_election, state.level, by = "state") %>% arrange(state)
head(total_df, 6)
```

**(h)** The plot shows that both total cases and total deaths are not relevant with election results.

```{r}
total_df <- total_df[complete.cases(total_df),]

ggplot(total_df, aes(x = tot_cases, y = tot_deaths, color = Election)) +
  geom_point()
```
