---
title: "HW1.Q4.Ko"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
```

## 4. 

```{r}
library(tidyverse)
library(palmerpenguins)
head(penguins,5)
```



**(a)** There seems to be a linear relationship between flipper length and body mass.

```{r}
ggplot(penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(colour = "red") +
  labs(x = "Flipper Length (in mm)", y = "Body Mass (in gram)", title = "A Scatterplot of Flipper Length vs Body Mass")
```

**(b)** There seems to be linear relationship between flipper length and body mass across all species. This scatterplot does not influence my answer to the previous part. 

```{r}
ggplot(penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species)) +
  geom_point(xlab = "Flipper Length (in mm)", ylab = "Body Mass (in gram)", title = "A Scatterplot of Flipper Length vs Body Mass across Species")
```

**(c)** YES. There also seems to be a reasonable linear relationship between flipper length and body mass for Gentoo penguins. 

```{r}
gentoo <- penguins %>%
  filter(species == "Gentoo")

ggplot(gentoo, aes(x = flipper_length_mm, y = body_mass_g, xlab = "Flipper Length (in mm)", ylab = "Body Mass (in gram)", title = "A Scatterplot of Flipper Length vs Body Mass of Gentoo penguins")) +
  geom_point()
```

**(d)** For Gentoo penguins, the correlationship between flipper length and body mass is 0.7026665, which is pretty high. This means flipper length and body mass is in proportional relationship. 

```{r}
cor(gentoo$flipper_length_mm, gentoo$body_mass_g, use = "complete.obs")
```

**(e)** $\hat{y} = -6787.281 + 54.623 * x$

```{r}
gentoo_result <- lm(body_mass_g ~ flipper_length_mm, data = gentoo)
summary(gentoo_result)
```

**(f)** The slope implies 1mm increase of flipper length is proportional 54.623 grams of increase in body mass.

**(g)** The intercept is abnormally small. Body mass cannot be less than zero when flipper length is 0.

**(h)**  R2 = 0.4937, which means that about 49.37% of the variation in body mass can be explained by flipper length. 

**(i)** $\hat{o} = 360.2$  is the estimated value for standard deviation. 


**(j)** The predicted body mass in grams is 5229.779. 

```{r}
y_hat = -6787.281 + 54.623 * 220
y_hat
```


**(k)**  0.4937402 

```{r}
gentoo.anova.tab <- anova(gentoo_result)
gentoo.anova.tab

SST <- sum(gentoo.anova.tab$"Sum Sq")
SSR <- gentoo.anova.tab$"Sum Sq"[1]
SSres <- gentoo.anova.tab$"Sum Sq"[2]

r_2 <- SSR / SST
r_2
```


**(l)** $ H_0: \beta_1 = 0$, $ H_a: \beta_1 \neq 0$


**(m)** We can derive f statistic from anova table.

```{r}
f_statistic <- gentoo.anova.tab$`F value`[1] 
round(f_statistic, 2)
```


**(n)** We can use two approaches: P-Value Approach, and Critical Value Approach.

- P-Value Approach: As P-value is 2.2e-16 * 2 < 0.05, so we can reject the null hypothesis.


- Critical Value Approach: As F* (Critical Value = 5.150187) < F-statistic (= 118.01), we can reject the null hypothesis.

```{r}
qf(0.975, 1, (nrow(gentoo) -2)) # CRITICAL VALUE
```


**(o)**  When flipper length increases by 1mm, the 95% confidence interval gives that the predicted body mass will increase within the range of (44.66777,    64.57724).
```{r}
confint(gentoo_result, level = 0.95)
```


**(p)** According to the result of previous question, there is 95 % chance of having B1 between (44.66777, 64.57724) and 0 is not within the interval. As a result, we can reject the null hypothesis stating that B1 = 0.



**(q)** Estimated mean body mass = 4137.22, 95% CI: (3954.446, 4319.993)
```{r}
gentooData <- data.frame(flipper_length_mm = 200)

predict(gentoo_result, gentooData, level = 0.95, interval = "confidence")
```


**(r)** (3401.121, 4873.319)
```{r}
predict(gentoo_result, gentooData, level = 0.95, interval = "prediction")
```


**(s)** $H_0: \beta_1 = 50$, $H_a: \beta_1 > 50$

- t-test statistic: 0.9194511, critical value: 1.657439 **

- As critical value > t-statistic, we cannot reject the null hypothesis  that predicted body mass increases by 50g. **

- As p-value (=0.179837) > 0.05, we cannot reject the null hypothesis that predicted body mass increases by 50g.**

- Therefore, from two approaches, we cannot identically reject the null hypothesis.**


```{r}
critical_value <- qt(0.95, nrow(gentoo) - 2) # ONE-SIDED TEST
critical_value

t_statistic <- (54.623 - 50) / 5.028
t_statistic

p_value <- 1 - pt(t_statistic, nrow(gentoo) - 2)
p_value
```