---
title: "HW1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
```

## 1

```{r cars}
library(tidyverse)
students <- read.table("students.txt", header = TRUE)
head(students, 5)
```

**(a)** Students column only contains index, so I removed it from the data.
```{r}
students <- select(students, -Student)
head(students,5)
```

**(b)**  Total 249 students.
```{r}
nrow(students)
```


**(c)** Total 12 missing entries in at least one of the columns.

```{r}
nrow(students[!complete.cases(students),])
students <- students[complete.cases(students),]
head(students,5)
```

**(d)** median gpa = 3.2, median study hours = 12

```{r}
students %>%
  summarize(median_GPA = median(GPA), median_studyhrs= median(StudyHrs))
```

**(e)** Female: mean study hours = 15.26471, standard deviation of study hours = 9.062937, median study hours = 12.5	
 Male: mean study hours = 14.74257, standard deviation of study hours = 10.315671	, median study hours = 12.0	 
 According to the result, female students tend to study a little bit more than male students, but male students have larger spread in study hours than female students.


```{r}
students %>%
  group_by(Gender) %>%
  summarize(mean(StudyHrs), sd(StudyHrs), median(StudyHrs))
```

**(f)** 

```{r}
students <- students %>% 
  mutate(PartyAnimal = ifelse(PartyNum > 8, "yes", "no"))
head(students,5)
```


**(g)** 

```{r}
students <- students %>% 
  mutate(GPA.cat = cut(GPA, breaks = c(-Inf, 3.0, 3.5, Inf), right = FALSE,
                                 labels = c("low", "moderate", "high")))
head(students,5)
```


**(h)** Total 29 students. 

```{r}
head(students %>% filter((GPA < 3.0) & (StudyHrs < 15) & (PartyNum > 8)),5)
```

**(i)** Low: 86, Moderate: 84, High: 67

```{r}
table(students$GPA.cat)
```


**(j)** 

```{r}
ggplot(students, aes(x = GPA.cat)) +
  geom_bar(xlab = "GPA levels", ylab = "Observations", title = "Number of Students Across GPA Levels", fill = "blue") +
  labs(title = "The number of students across GPA Categories")
```

**(k)** 

```{r}
new_students <- students %>% 
  group_by(GPA.cat) %>% 
  summarize(Counts=n()) %>% 
  mutate(Percent=Counts/nrow(students)) %>%
  select(-Counts)
new_students

ggplot(new_students, aes(x = GPA.cat, y = Percent)) +
  geom_bar(stat ="identity", fill = "orange") +
  labs(title = "Percentage of Students Across GPA Categories")
```

**(l)** 
```{r}
table(students$GPA.cat, students$Gender)
```


**(m)** Except for low GPA category, female students to have moderate ~ high GPAs than male students.

```{r}
round(table(students$GPA.cat, students$Gender) %>% prop.table(),2)
```


**(n)**

```{r}
ggplot(students,aes(x=Gender, fill=GPA.cat)) + 
  geom_bar(position = "fill") + 
  labs(title = "Proportion of GPA Categories of All Sex")
```


**(o)** The majority of both female and male students were non-smokers.

```{r}
ggplot(students,aes(x=Gender, fill=Smoke)) + 
  geom_bar(position = "fill") +
  labs(title = "Proportion of Smokers in All Sex")
```


**(p)** The more time spent studying, the better GPA grades.
```{r}
ggplot(students, aes(x= GPA.cat, y = StudyHrs)) +
  geom_point() +
  labs(title = "Number of Studying Hours Across GPA Categories")
```

**(q)** 

```{r}
ggplot(students, aes(x= GPA.cat, y = StudyHrs, size = PartyNum)) +
  geom_point() +
  labs(title = "Number of Studying Hours and Party Numbers Across GPA Categories")
```

**(r)**

```{r}
ggplot(students, aes(x= GPA.cat, y = StudyHrs, size = PartyNum, color = Smoke)) +
  geom_point() +
  labs(title = "Number of Studying Hours Across GPA Categories and Smoking Status")

```